---
title: "BD_BIDS_Converter"
author: "Niklas Wulms"
date: "7/4/2019"
output: html_document
---

#### optional: libraries to install

```{r eval=FALSE}
install.packages("stringr")
install.packages("tidyverse")
install.packages("devtools")
devtools::install_github("muschellij2/dcm2niir")
```

#### load libraries

```{r}
library(stringr)
library(tidyr)
library(devtools)
library(dcm2niir)
```

```{r eval=FALSE}
install_dcm2nii(lib.loc=NULL, overwrite = FALSE, from_source = TRUE, jpeg = FALSE, progdir = NULL)
```


# set here your start folder

```{r}
start_dir <- ("/media/niklas/spaceC/BIDS_Convert_test") 
setwd(start_dir)
```

```{r setup}

knitr::opts_knit$set(root.dir = start_dir)

```


#### creation of output folders

```{r}
dicom_dir <- paste0(file.path("dicom"))
dir.create("nii_temp")
dir.create("nii")
dir.create("codebooks")
```

#### creation of codebooks

```{r}
timepoints <- list(old = c("ses1", "ses2", "ses3", "ses3_plus", "ses4", "ses4_plus"), 
                         new = c("ses1", "ses2", "ses3", "ses3_plus", "ses4", "ses4_plus"))

sequence <- list(old = c("anat/T1w", "anat/T2w", "anat/T2star", "anat/FLAIR",
                               "func/rest", "func/epi_bold",
                               "dwi/DTI",
                               "other/T2ffe"),
                       new = c("anat/T1w", "anat/T2w", "anat/T2star", "anat/FLAIR",
                               "func/rest", "func/epi_bold",
                               "dwi/DTI",
                               "other/T2ffe"))
string_replace <- list(old = c("unwanted_prefix"),
                             new = c("replacement"))

codebooks <- list(timepoints, sequence, string_replace)
codebook_names <- c("timepoints", "sequence", "string_replace")
```

#### writing codebooks as csv

```{r}
a <- 1
 for (i in codebooks) {
    print(codebook_names[a])
   print(paste0("codebooks/", codebook_names[a], ".csv"))
    print(i)
    write.table(i, paste0("codebooks/", codebook_names[a], ".csv"), 
            row.names = FALSE,
            quote = FALSE,
            sep = ";")
    a <- a + 1
   }

```

#### Fill in your information into the _codebooks_.

Use LibreOffice, Excel, or some other editor. Then it is time to read it in.

#### Indexing of dicom images

compare which folders are done and which are not done.

```{r}
dicoms <- dir(dicom_dir, full.names = TRUE)

timepoint_path <- list.dirs("dicom", 
    recursive = FALSE, 
    full.names = TRUE)

dicoms <- unlist(lapply(timepoint_path, FUN = dir, 
                 recursive = FALSE, 
                 full.names = TRUE))

dicoms_done <- unlist(lapply(timepoint_path, FUN = dir, 
                 pattern = "_done", 
                 recursive = FALSE, 
                 full.names = TRUE))

dicoms <- setdiff(dicoms, dicoms_done)
```

# Main step 2: Nii conversion

here a loop reads in the dicoms (that dont have the suffix "_done") and converts them. Then changes the folder name to "_done".

#### flags

-ba y or n - turns on BIDS and anonymization
-o "path" - gives the output path
-z - turns on conversion
-f - filename information

```{r}

output_path <- str_replace(dicoms, "dicom", "nii_temp") %>%
  str_replace(regex(",bidirect", ignore_case = TRUE), "")

lapply(output_path, dir.create, recursive=TRUE)

for (i in 1:length(dicoms)) {
  print(dicoms[i])
  dcm2nii(dicoms[i], 
          copy_files = FALSE,
          opts = paste0("-ba y ", "-o ", output_path[i], " -z y", " -f %d"))
  
  file.rename(dicoms[i], paste0(dicoms[i],"_done"))
}

```

## Now that your files are converted and anonymized we take care of getting the data into the BIDS format and move them from the nii_temp folder to the nii folder.

# Step 3: BIDS formatting and moving

```{r}
nii_temp_path <- list.files("nii_temp", 
                     recursive = TRUE,
                     full.names = TRUE)
```







