---
  title: "BiDirect BIDS Overview"
output: 
  flexdashboard::flex_dashboard:
  vertical_layout: scroll
source_code: embed
---
  
  ```{r setup, include=FALSE}
library(flexdashboard)
library(stringr)
library(tidyr)
library(stringi)
library(dplyr)
library(printr)
library(DT)
library(forcats)
library(lubridate)
library(highcharter)


knitr::opts_chunk$set(echo = TRUE)

# On Linux
working_dir <- ("/mnt/TB8Drive/Bidirect_Neuroimaging/") 
knitr::opts_knit$set(root.dir = working_dir)

setwd(working_dir)
```

```{r echo=FALSE}
load("json_all.Rdata")
json_meta_all2 <- json_meta_all2 %>% ungroup() %>%
  mutate(PatientID = str_extract(PatientID, "[:digit:]{5}"),
         PatientName = str_extract(PatientID, "[:digit:]{5}"),
         AcquisitionDate = ymd_hms(AcquisitionDateTime) %>% date())

json_short <- json_meta_all2 %>%
  select(subject, session, AcquisitionDate, PatientBirthDate, PatientSex, PatientWeight) %>% unique()

```

```{r include=FALSE}
dicoms <- dir("DICOM", full.names = TRUE)

dicoms <- unlist(lapply(dicoms, FUN = dir, 
                        recursive = FALSE, 
                        full.names = TRUE)) 

dicoms_to_process <- dicoms


# Creation of pathnames for temporary output / Cleaning of filenames (stringr package)
nii_temp_path <-
  str_replace(dicoms_to_process, "DICOM", "NII_temp") %>%
  str_replace_all(regex("(bidirect_plus|bidirect-plus|bidiect_plus)", ignore_case = TRUE),
                  "") %>%
  str_replace_all(regex("(_bidirect|bidirect)", ignore_case = TRUE), "") %>%
  str_replace_all(
    regex(
      "(bibirect|didirect|_bidrect|bi direct|bdirect|bi_direct)",
      ignore_case = TRUE
    ),
    ""
  ) %>%
  str_replace(regex(", |,_|,,|,|\\.|\\__"), "") %>%
  str_replace(regex("10646_plus", ignore_case = TRUE), "10646") %>%
  str_replace("30224neu", "30224") %>%
  str_replace("30250_incl DIR-Sequenz", "30250") %>%
  str_replace_all(regex("plus", ignore_case = TRUE), "plus") %>%
  str_replace("10738eigentlich_|_RS|RS|T2TSE|ABBRUCH", "")


dicoms_mapping <-
  cbind(dicoms_to_process, nii_temp_path, deparse.level = 0)
dicoms_mapping <- data.frame(dicoms = dicoms_to_process,
                             nii_temp = nii_temp_path,
                             stringsAsFactors = FALSE)

survey_order <- c("Baseline", "FollowUp", "FollowUp2", "FollowUp3", "FollowUp2_plus", "FollowUp3_plus")

dicoms_mapping <- dicoms_mapping %>%
  mutate(id = str_extract(nii_temp, "[:digit:]{5}"),
         cohort = str_sub(id, 1, 1),
         cohort = fct_recode(cohort, "depression" = "1", "cardiovascular disease" = "2", "general_population" = "3") %>%
           fct_relevel("general_population", "depression", "cardiovascular disease"),
         survey = str_remove_all(nii_temp, "[:digit:]{5}|NII_temp/|/") %>% as.factor(),
         survey = fct_relevel(survey, survey_order),
         n = 1)



```


Overview
=================
  - here you find the information about BIDS type and new sequence name

Column {data-width=50}
--------
  
  ### Folders
  
  ```{r echo=FALSE}
folder_count <- length(dicoms) %>% round(0)

valueBox(folder_count, 
         icon = "fa-folder-open", 
         caption = "DICOM folders", 
         color = "green")
```


### Total converted files

```{r echo=FALSE}
converted_count <- length(json_meta_all2$new_nii3) %>% round(0)

valueBox(converted_count, 
         icon = "fa-angle-double-right", 
         caption = "Converted NII files", 
         color = "green")
```

### Count plausible

```{r echo=FALSE}
plausible_base <- json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "highres") == 0)

plausible_base_count <- str_detect(plausible_base$bids_type, "implausible", negate = TRUE) %>% sum()

valueBox(plausible_base_count, 
         icon = "fa-smile-beam", 
         caption = "Plausible files - Base", 
         color = "green")
```

### Count plausible Plus

```{r echo=FALSE}
plausible_plus <- json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "highres") == 1)

plausible_plus_count <- str_detect(plausible_plus$bids_type, "implausible", negate = TRUE) %>% sum()

valueBox(plausible_plus_count, 
         icon = "fa-smile-beam", 
         caption = "Plausible files - Plus ", 
         color = "green")
```

### Count implausible

```{r echo=FALSE}
implausible <- json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 1)

implausible_count <- str_detect(implausible$bids_type, "implausible") %>% sum()

valueBox(implausible_count, 
         icon = "fa-minus-square", 
         caption = "Implausible files", 
         color = "green")
```


Column {data-width=150}
--------
  
  ### Plausible Base 
  
  ```{r echo=FALSE}

hchart(plausible_base$bids_type, "column")
```



### Plausible Plus

```{r echo=FALSE}


hchart(plausible_plus$bids_type, "column")
```


### Implausible

```{r echo=FALSE}

hchart(implausible$bids_type, "column")
```


Column {data-width=150}
-----------------------------------------------------------------------
  
  ### Overview of JSONS per participant and survey of base_protocol
  
  ```{r echo=FALSE}

json_meta_all2 %>%
  ungroup() %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(plus , "plus") == 0) %>%
  add_count(bids_type, name = "total") %>%
  group_by(bids_type, plus, total, session) %>%
  count() %>%
  spread(session, n)%>%
  ungroup() %>%
  arrange(plus) %>%
  DT::datatable(caption = 'Table 2: N of participants per survey (total) and separately by cohort.',
                colnames = c('Survey' = 1),
                rownames = FALSE,
                options = list(pageLength = 20))

```

### Overview of JSONS per participant and survey of plus_protocol

```{r echo=FALSE}

json_meta_all2 %>%
  ungroup() %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(plus , "plus") == 1) %>%
  add_count(bids_type, name = "total") %>%
  group_by(bids_type, plus, total, session) %>%
  count() %>%
  spread(session, n)%>%
  ungroup() %>%
  arrange(plus) %>%
  DT::datatable(caption = 'Table 2: N of participants per survey (total) and separately by cohort.',
                colnames = c('Survey' = 1),
                rownames = FALSE,
                options = list(pageLength = 20))

```

Input data
==================
  
  Here you find the count of all DICOM folders at each survey.

Column {data-width=250}
-----------------------------------------------------------------------
  
  ### List of folders per subject - Conversion from DICOM into the NIfTI folder
  
  
  
  ```{r echo=FALSE}
DT::datatable(dicoms_mapping,
              caption = 'Table 1: This is the old and the new foldername (where the converted files are saved).',
              colnames = c('DICOM folder' = 1, "NIfTI" = 2),
              rownames = FALSE,
              options = list(pageLength = 20))


```

Column {data-width=150}
-----------------------------------------------------------------------
  
  ### Removed appendices - these are removed from the filenames to enable a clean structure in the subject folders
  
  ```{r echo=FALSE}
dicoms_mapping %>%
  select(dicoms) %>%
  mutate(dicoms = str_remove_all(dicoms, "DICOM/|Baseline/|FollowUp/|FollowUp2/|FollowUp3/|FollowUp2_(p|P)lus/|FollowUp3_(p|P)lus/") %>%
           str_remove("[:digit:]{5}")) %>%
  count(dicoms) %>%
  DT::datatable(caption = 'Table 2: Redundant appendices, that are removed to clean up the filenames',
                colnames = c('Removed Appendices' = 1),
                rownames = FALSE,
                options = list(pageLength = 15))
```


### Not identified filenames - This table should be empty! Otherwise the filename was not equal to 5 digits.

```{r echo=FALSE}
dicoms_mapping %>%
  select(nii_temp) %>%
  filter(str_detect(nii_temp, pattern = "/[:digit:]{5}$", negate = TRUE) == 1) %>%
  DT::datatable(caption = 'Table 3: Identified strings that do not match 5 digits in filename',
                colnames = c('Survey' = 1),
                rownames = FALSE,
                options = list(pageLength = 8))
```

Column {data-width=200}
-----------------------------------------------------------------------
  
  ### Summary table per survey and cohort
  
  ```{r echo=FALSE}


dicoms_mapping %>%
  select(survey, cohort) %>%
  add_count(survey, name = "total") %>%
  group_by_all() %>%
  count() %>%
  spread(cohort, n) %>%
  DT::datatable(caption = 'Table 4: N of participants per survey (total) and separately by cohort.',
                colnames = c('Survey' = 1),
                rownames = FALSE,
                options = list(pageLength = 8))


input_summary <- dicoms_mapping %>%
  count(survey, cohort)


hchart(input_summary, "column", hcaes(x = survey, y = n, group = cohort))
```






File renaming
=================
  - here you find the information about renaming the old sequence names to the new sequence_clean


Column {data-width=150}
-----------------------------------------------------------------------
  
  ### JSON mapping (sequence name vs BIDS name) - Base - plausible sequences (include / keep)
  
  ```{r echo=FALSE}
json_meta_all2 %>%
  ungroup() %>%
  filter(str_detect(plus, "plus") == 0) %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  select(bids_type, sequence, sequence_clean) %>%
  arrange(bids_type) %>%
  group_by_all() %>%
  count() %>%
  DT::datatable(caption = 'Table 1: Sequences (N) BASE of participants per survey (total) and separately by cohort.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                options = list(pageLength = 20))
```

### JSON mapping (sequence name vs BIDS name) - Plus - plausible sequences (include / keep)

```{r echo=FALSE}
json_meta_all2 %>%
  ungroup() %>%
  filter(str_detect(plus, "plus") == 1) %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(sequence, "e(2|3|4|5|6|7)") == 0) %>%
  select(bids_type, sequence, sequence_clean) %>%
  arrange(bids_type) %>%
  group_by_all() %>%
  count() %>%
  DT::datatable(caption = 'Table 2: Sequences (N) PLUS of participants per survey (total) and separately by cohort.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                options = list(pageLength = 20))
```

Column {data-width=150}
-----------------------------------------------------------------------
  
  ### JSON mapping (sequence name vs BIDS name) - implausible sequences (exclude / delete)
  
  ```{r echo=FALSE}
json_meta_all2 %>%
  ungroup() %>%
  filter(str_detect(bids_type, "implausible") == 1) %>%
  select(bids_type, sequence, sequence_clean) %>%
  arrange(bids_type) %>%
  group_by_all() %>%
  count() %>%
  DT::datatable(caption = 'Table 3: Sequences (N) IMPLAUSIBLE of participants per survey (total) and separately by cohort.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                options = list(pageLength = 20))
```



Duplicates
================
  
  Column {data-width=300}
-----------------------------------------------------------------------
  
  ### Duplicates based on BIDS type
  
  ```{r echo=FALSE}
json_meta_all2 %>%
  select(subject, session, bids_type) %>%
  group_by_all() %>% count() %>% filter(n != 1 & n != 7) %>%
  filter(str_detect(bids_type, "implausible|Smartbrains|T2star_ph_highres|T2_star_highres") == 0)  %>% left_join(json_meta_all2) %>%
  select(session, session, new_nii3) %>%
  DT::datatable(caption = 'Table 1: Duplicate Sequences, filtered by bids_type.',
                colnames = c('Filename' = 4),
                rownames = FALSE,
                options = list(pageLength = 20))
```

### Duplicate sequences (implausible)

```{r echo=FALSE}
json_meta_all2 %>%
  select(session, subject, bids_type, session, new_nii3) %>%
  filter(str_detect(new_nii3, "-(a|b|c)") == 1 & str_detect(new_nii3, "implausible") == 1) %>%
  DT::datatable(caption = 'Table 2: Duplicate sequences (implausible) indicated by a -a/b/c in filename.',
                colnames = c('Filename' = 4),
                rownames = FALSE,
                options = list(pageLength = 20))
```

Column {data-width=250}
-----------------------------------------------------------------------
  
  ### Duplicate sequences (no unique filename) - empty is good!
  
  ```{r echo=FALSE}
json_meta_all2 %>%
  select(new_nii3) %>%
  group_by_all() %>%
  count() %>% filter (n != 1) %>%
  DT::datatable(caption = 'Table 3: Sequences, that have the same filename.',
                colnames = c('ID' = 1),
                rownames = FALSE,
                options = list(pageLength = 20))
```


ID plausibility
==================
  - identifiable information (gender, age, weight, acquisition date)

Column {data-width=150}
-----------------------------------------------------------------------
  
  ### ID differences (filename, PatientID, PatientName) - empty is good!
  
  ```{r echo=FALSE}

json_meta_all2 %>%
  select(subject, PatientID, PatientName) %>% unique() %>%
  group_by_all() %>% count() %>%
  filter(n > 1) %>%
  select(-n) %>%
  DT::datatable(caption = 'Table 1: Participants with differences between the id variables',
                colnames = c('ID' = 1),
                rownames = FALSE,
                options = list(pageLength = 20))


```

### Implausible Birthdates

```{r echo=FALSE}
json_meta_all2 %>%
  select(subject, PatientBirthDate) %>%
  filter(str_detect(PatientBirthDate, "-07-01") == 0) %>%
  arrange(subject) %>%
  group_by_all() %>%   unique() %>% ungroup () %>% add_count(subject) %>%
  #  filter(n != 1) %>%
  left_join(json_short) %>%
  select(-PatientSex, -PatientWeight, -n) %>%
  DT::datatable(caption = 'Table 2: Participants with implausible birthdate (not -07-01 coded)',
                colnames = c('ID' = 1),
                rownames = FALSE,
                options = list(pageLength = 10))
```

### Change in Birthdates between Surveys

```{r echo=FALSE}
json_meta_all2 %>%
  select(subject, PatientBirthDate) %>%
  arrange(subject) %>%
  group_by_all() %>%   unique() %>% ungroup () %>% add_count(subject) %>%
  filter(n != 1) %>%
  left_join(json_short) %>%
  select(-PatientSex, -PatientWeight, -n) %>%
  DT::datatable(caption = 'Table 3: Participants with a change in BirthDate',
                colnames = c('ID' = 1),
                rownames = FALSE,
                options = list(pageLength = 10))
```

### Change in Sex between Surveys

```{r echo=FALSE}
json_meta_all2 %>%
  select(subject, PatientSex) %>%
  arrange(subject) %>%
  group_by_all() %>%   unique() %>% ungroup() %>% add_count(subject) %>%
  filter(n != 1) %>%
  left_join(json_short) %>%
  select(-PatientBirthDate, -PatientWeight, -n) %>%
  DT::datatable(caption = 'Table 4: Participants with a change in Sex',
                colnames = c('ID' = 1),
                rownames = FALSE,
                options = list(pageLength = 10))
```

### Change in AcquisitionDate between Surveys

```{r echo=FALSE}
json_meta_all2 %>%
  select(subject, session, AcquisitionDate) %>%
  arrange(subject) %>%
  group_by_all() %>%   unique() %>% group_by(subject, session) %>% count() %>% 
  filter(n != 1) %>%
  left_join(json_short) %>%
  select(-PatientBirthDate, -PatientWeight, -PatientSex, -n) %>%
  DT::datatable(caption = 'Table 5: Participants with a change in AcquisitionDate',
                colnames = c('ID' = 1),
                rownames = FALSE,
                options = list(pageLength = 10))
```



MRI parameters - Base
===================
  
  Here you can explore the physical properties of the sequence parameters

Column
------------------------
  
  ### T1w
  
  ```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "T1w") == 1) %>%
  filter(str_detect(plus, "plus") == 0) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 3) %>%  
  mutate_at(c("PixelBandwidth"), round, -1) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 1: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(256,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))

```

### FLAIR

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "FLAIR") == 1) %>%
  filter(str_detect(plus, "plus") == 0) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 3) %>% 
  mutate_at(c("PixelBandwidth"), round, -2) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 2: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(257, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(512,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(257, c('lightblue')))

```

### T2w

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "T2w/") == 1) %>%
  filter(str_detect(plus, "plus") == 0) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 2) %>%  
  mutate_at(c("PixelBandwidth"), round, -1) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 3: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(319, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(512,c('lightblue')))%>%
  formatStyle('RepetitionTime', backgroundColor = styleEqual(3,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(319, c('lightblue')))

```

### T2w_star

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "T2w_star") == 1) %>%
  filter(str_detect(plus, "plus") == 0) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 2) %>%  
  mutate_at(c("PixelBandwidth"), round, -1) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 4: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(205, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(512,c('lightblue')))%>%
  formatStyle('SliceGap', backgroundColor = styleEqual(5,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(205, c('lightblue')))

```

### DWI

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "DTI") == 1) %>%
  filter(str_detect(plus, "plus") == 0) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%  
  mutate_at(c("PixelBandwidth"), round, -1) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 5: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) 

```

### rest

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "rest") == 1) %>%
  filter(str_detect(plus, "plus") == 0) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%  
  mutate_at(c("PixelBandwidth"), round, -2) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 6: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20))

```

### Emotional Faces

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "EF") == 1) %>%
  filter(str_detect(plus, "plus") == 0) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%  
  mutate_at(c("PixelBandwidth"), round, -1) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 7: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(256,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))

```

MRI parameters - Plus
===================
  
  Column
------------------------
  
  ### T1w highres
  
  ```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "T1w_highres") == 1) %>%
  filter(str_detect(plus, "plus") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>% 
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 3) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 1: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(512,c('lightblue')))%>%
  formatStyle('SliceGap', backgroundColor = styleEqual(0.5,c('lightblue')))%>%
  formatStyle('SliceThickness', backgroundColor = styleEqual(1, c('lightblue')))
```

### FLAIR highres

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "FLAIR_highres") == 1) %>%
  filter(str_detect(plus, "plus") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>% 
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 2: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('SliceThickness', backgroundColor = styleEqual(1.2, c('lightblue'))) %>%
  formatStyle('SliceGap', backgroundColor = styleEqual(0.6,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))
```

### T2star highres

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "T2star_ph") == 1) %>%
  filter(str_detect(plus, "plus") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>% 
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 2) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 3: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) 
```

### T2star ph highres

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "T2star_h") == 1) %>%
  filter(str_detect(plus, "plus") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>% 
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 2) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 4: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) 
```

### T2w highres

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 0) %>%
  filter(str_detect(bids_type, "T2w_highres") == 1) %>%
  filter(str_detect(plus, "plus") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>% 
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%  
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 5: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(228, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(512, c('lightblue')))%>%
  formatStyle('RepetitionTime', backgroundColor = styleEqual(3, c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(228, c('lightblue')))
```



MRI parameters - implausible
===================
  
  Column
------------------------
  
  ### T1w
  
  ```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 1) %>%
  filter(str_detect(bids_type, "T1w") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 1: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(256,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))
```

### FLAIR

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 1) %>%
  filter(str_detect(bids_type, "flair") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 2: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(256,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))
```


### T2w_Star

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 1) %>%
  filter(str_detect(bids_type, "T2w_star") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 3: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(256,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))
```


### dwi

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 1) %>%
  filter(str_detect(bids_type, "dwi") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 4: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(256,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))
```

### Strange

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 1) %>%
  filter(str_detect(bids_type, "Strange") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 5: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(256,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))
```

### Smartbrains

```{r echo=FALSE}
json_meta_all2 %>%
  filter(str_detect(bids_type, "implausible") == 1) %>%
  filter(str_detect(bids_type, "Smart") == 1) %>%
  select(bids_type, AcqMatrix, ReconMatrix, SliceThickness, SliceGap, RepetitionTime, 
         EchoTime, EchoTrain, FlipAngle, PhaseEncodingSteps, PixelBandwidth, 
         SAR, PhaseDirection, Averages, PartialFourier, MRType, SoftwareVersions) %>%
  mutate_at(c("EchoTime", "PartialFourier", "SAR"), round, 2) %>%
  mutate_at(c("RepetitionTime"), round, 4) %>%
  group_by_all() %>% count() %>% arrange(desc(n)) %>% select(bids_type, n, everything()) %>%
  DT::datatable(caption = 'Table 6: Sequences, filtered by bids_type.',
                colnames = c('BIDS_type' = 1),
                rownames = FALSE,
                filter = 'top', 
                options = list(pageLength = 20)) %>%
  formatStyle('AcqMatrix', backgroundColor = styleEqual(255, c('lightblue'))) %>%
  formatStyle('ReconMatrix', backgroundColor = styleEqual(256,c('lightblue')))%>%
  formatStyle('PhaseEncodingSteps', backgroundColor = styleEqual(255, c('lightblue')))
```


MRI QC
===================
  
  Column
------------------------
  
  Container use possible!  
  ETA: about 50 min. per Subject/Session  

Quality metrices for T1w, T2w and functional sequences  



fMRIprep
===================
  
  Column
------------------------
  
  Container use possible!  
  ETA: about 11 h per Subject (freesurfer processing pipeline)  

- T1w and functional sequences processing pipeline



Derivatives
===================
  
  Column
------------------------
  
  Already calculated:  
  
  _T1w_:  VBM (CAT12)  
_DTI_: PSMD Marker, FA (native/normalized), MD (native/normalized)  

_FLAIR_: (on 201 subjects) BIANCA, LST Toolbox, LesionBrain, CAT12 WMH detection  
planned: DeepMedic, OASIS


